---
title: "mids-203-project"
output: html_document
date: "2026-04-09"
---

```{r cars}
# Load libraries
library(ggplot2)
library(car)
library(lmtest)

# Read CSV (adjust path as needed)
df <- read.csv("merged_raw_all_years.csv")
dim(df)
```

Added column names bc i got a little confused -Malachi
```{r}
colnames(df)[grepl("PFL|FSS|CDA|CHA|FGA|NDA", colnames(df))]
```
First task: examine the data for cleanliness issues

- Realizing that a lot of the variables in the dataset are missing like 50% of the rows...so let's first rank all the possible Y variables (in 'ecosystem vitality on page 3') and X variables (in 'climate change on page 4') based on how many NA rows there are, then choose based on a tradeoff between relevance and # of missing rows.
- I'm using 2019, which is the last year with fisheries data (see page 130/131)

```{r}
ecosystem_vars <- c(
  # Biodiversity & Habitat
  "MKP", "MHP", "MPE", "PAR", "SPI", "TBN", "TKP", "PAE", "PHL", "RLI", "SHI", "BER",
  
  # Forests
  "PFL", "IFL", "FCL", "TCG", "FLI",
  
  # Fisheries
  "FSS", "FCD", "BTZ", "BTO", "RMS",
  
  # Air Pollution
  "OEB", "OEC", "NXA", "SDA",
  
  # Agriculture
  "SNM", "PSU", "PRS", "RCY",
  
  # Water Resources
  "WWG", "WWC", "WWT", "WWR"
)

eco_col_matches <- colnames(df)[
  grepl(paste(ecosystem_vars, collapse = "|"), colnames(df)) &
    grepl("2019$", colnames(df))
]

df_ecosystem = df[, eco_col_matches]

# sort each column in the ecosystem vitality (ECO) category by the number of NAs in the year 2019
sort(colSums(is.na(df_ecosystem)))

```
Most relevant Y-variables would be:
  - PFL (primary forest loss) - 137 missing rows out of 220
- Alternative: FCL (74 missing rows)
- FSS (fish stock status) - 102 missing rows out of 220
- Alternative: RLI/SHI - 2 and 43 missing rows
- Could consider using TBN (terrestrial biome protection/biodiversity/ecosystem vitality) - not ideal but it has no missing data

Now to look at the x-variables:
  
```{r}
climate_vars <- c(
  # Climate Change Mitigation
  "CDA",  # Adjusted emissions growth rate for CO2
  "CDF",  # CO2 growth rate (country-specific targets)
  "CHA",  # Adjusted emissions growth rate for methane
  "FGA",  # Adjusted emissions growth rate for F-gases
  "NDA",  # Adjusted emissions growth rate for nitrous oxide
  "BCA",  # Adjusted emissions growth rate for black carbon
  "LUF",  # Net carbon fluxes due to land cover change
  "GTI",  # GHG growth rate adjusted by emissions intensity
  "GTP",  # GHG growth rate adjusted by per capita emissions
  "GHN",  # Projected emissions in 2050
  "CBP"   # Projected cumulative emissions to 2050 relative to carbon budget,
)

climate_col_matches <- colnames(df)[
  grepl(paste(climate_vars, collapse = "|"), colnames(df)) &
    grepl("2019$", colnames(df))
]

df_climate = df[, climate_col_matches]

# sort each column in the ecosystem vitality (ECO) category by the number of NAs in the year 2019
sort(colSums(is.na(df_climate)))


```

The x-variables we might use are basically all missing 20-30 rows, not bad. We can then choose based purely on what's most relevant:
- CDO (carbon dioxide emissions)
- CH4 (methane emissions)
- FOG (F-gas emissions)
- NOT (N2O emissions)

We can also investigate how much missing data is in the GDP for 2019:
```{r}
sum(is.na(df[, 'GDP.raw.2019']))
```

What if we looked at only our best variables of interest and saw how small that dataset would be?

```{r}
vars_y <- c("PFL", "FSS")
vars_x <- c("CDO", "CH4", "FOG", "NOT")
vars_z <- c("GDP")
patterns <- c(vars_y,vars_x,vars_z)


cols_matched <- colnames(df)[
  grepl(paste(patterns, collapse = "|"), colnames(df)) &
  grepl("2019$", colnames(df))
]

df_2019 <- df[, c("code", "iso", "country", cols_matched)]
# How much data are we left with if we remove all rows with NA in any of these columns of interest?

df_2019_clean <- na.omit(df_2019)
dim(df_2019_clean)
summary(df_2019_clean[, cols_matched])
```
It appears that for 2019, which is the last year that we still have fisheries data (FSS), we only have 43 countries that have data for all the variables of interest.

Checking pairwise for countries if we just do a direct X and Y relationship
```{r}
vars_y <- c("PFL", "FSS")
vars_x <- c("CDA", "CHA", "FGA", "NDA")
control <- "GDP"
year <- "2019"

pair_2019 <- do.call(rbind, lapply(vars_y, function(yv) {
  do.call(rbind, lapply(vars_x, function(xv) {
    cols <- c(
      paste0(yv, ".raw.", year),
      paste0(xv, ".raw.", year),
      paste0(control, ".raw.", year)
    )
    
    temp <- df[, c("country", cols)]
    
    data.frame(
      y_var = yv,
      x_var = xv,
      year = as.integer(year),
      n_countries = nrow(na.omit(temp))
    )
  }))
}))

pair_2019[order(-pair_2019$n_countries), ]
```

Checking Year overlaps
```{r}
vars_y <- c("PFL", "FSS")
vars_x <- c("CDA", "CHA", "FGA", "NDA")

get_years <- function(var, data) {
  cols <- colnames(data)[grepl(paste0("^", var, "\\.raw\\."), colnames(data))]
  sub(paste0("^", var, "\\.raw\\.(\\d{4})$"), "\\1", cols)
}

count_pair_nonmissing <- function(y_var, x_var, year, data) {
  y_col <- paste0(y_var, ".raw.", year)
  x_col <- paste0(x_var, ".raw.", year)
  
  if (!(y_col %in% colnames(data)) || !(x_col %in% colnames(data))) return(NA_integer_)
  
  sum(!is.na(data[[y_col]]) & !is.na(data[[x_col]]))
}

pair_results <- do.call(rbind, lapply(vars_y, function(yv) {
  do.call(rbind, lapply(vars_x, function(xv) {
    
    overlap_years <- sort(intersect(get_years(yv, df), get_years(xv, df)))
    
    if (length(overlap_years) == 0) {
      return(data.frame(
        y_var = yv,
        x_var = xv,
        n_overlap_years = 0,
        overlap_years = NA_character_,
        best_year = NA_character_,
        best_n_complete = NA_integer_
      ))
    }
    
    counts <- sapply(overlap_years, function(yr) count_pair_nonmissing(yv, xv, yr, df))
    best_idx <- which.max(counts)
    
    data.frame(
      y_var = yv,
      x_var = xv,
      n_overlap_years = length(overlap_years),
      overlap_years = paste(overlap_years, collapse = ", "),
      best_year = overlap_years[best_idx],
      best_n_complete = counts[best_idx]
    )
  }))
}))

pair_results[order(-pair_results$best_n_complete), ]
```

---

## Variable Selection Decision

```{r variable-selection-stats}
n_fcl     <- sum(!is.na(df[["FCL.raw.2012"]]))
n_pfl     <- sum(!is.na(df[["PFL.raw.2012"]]))
r_fcl_pfl <- round(cor(df[["FCL.raw.2012"]], df[["PFL.raw.2012"]],
                        use = "complete.obs"), 3)

temp <- data.frame(
  POP     = df[["POP.raw.2012"]],
  CDO     = df[["CDO.raw.2012"]],
  NOX     = df[["NOX.raw.2012"]],
  SO2     = df[["SO2.raw.2012"]],
  CH4     = df[["CH4.raw.2012"]],
  FCL     = df[["FCL.raw.2012"]],
  GDP     = df[["GDP.raw.2012"]],
  HPE     = df[["HPE.raw.2012"]],
  SNM     = df[["SNM.raw.2012"]],
  GDP_pc  = df[["GPC.raw.2012"]]
)
temp$log_CDO <- log(pmax(temp$CDO, 1e-10))
temp$log_NOX <- log(pmax(temp$NOX, 1e-10))
temp$log_SO2 <- log(pmax(temp$SO2, 1e-10))
temp$log_CH4 <- log(pmax(temp$CH4, 1e-10))
temp$log_FCL <- log(pmax(temp$FCL, 1e-10))
temp$log_GDP <- log(pmax(temp$GDP, 1e-10))
temp$log_POP <- log(pmax(temp$POP, 1e-10))
temp$log_SNM <- log(pmax(temp$SNM, 1e-10))
temp <- na.omit(temp)

r_cdo_fcl <- round(cor(temp$log_CDO, temp$log_FCL), 3)
r_so2_fcl <- round(cor(temp$log_SO2, temp$log_FCL), 3)
r_ch4_fcl <- round(cor(temp$log_CH4, temp$log_FCL), 3)
r_snm_fcl <- round(cor(temp$log_SNM, temp$log_FCL), 3)
r_hpe_fcl <- round(cor(temp$HPE,     temp$log_FCL), 3)
r_cdo_gdp <- round(cor(temp$log_CDO, temp$log_GDP), 3)
r_cdo_so2 <- round(cor(temp$log_CDO, temp$log_SO2), 3)
r_cdo_ch4 <- round(cor(temp$log_CDO, temp$log_CH4), 3)
r_cdo_nox <- round(cor(temp$log_CDO, temp$log_NOX), 3)
r_cdo_snm <- round(cor(temp$log_CDO, temp$log_SNM), 3)

cat("FCL complete cases (2012):", n_fcl, "\n")
cat("PFL complete cases (2012):", n_pfl, "\n")
cat("r(FCL, PFL):", r_fcl_pfl, "\n")
cat("r(log_CDO, log_FCL):", r_cdo_fcl, "\n")
cat("r(log_SO2, log_FCL):", r_so2_fcl, "\n")
cat("r(log_CH4, log_FCL):", r_ch4_fcl, "\n")
cat("r(HPE,     log_FCL):", r_hpe_fcl, "\n")
cat("r(log_SNM, log_FCL):", r_snm_fcl, "\n")
cat("r(log_CDO, log_GDP):", r_cdo_gdp, "\n")
cat("r(log_CDO, log_SO2):", r_cdo_so2, "\n")
cat("r(log_CDO, log_SNM):", r_cdo_snm, "\n")
```

**Y: FCL (tree cover loss weighted by permanency)**
FCL gives `r n_fcl` complete cases vs `r n_pfl` for PFL. Both capture
ecosystem degradation from deforestation and are highly correlated
(r = `r r_fcl_pfl`). FCL is preferred purely for statistical power.

**Primary X: log(CDO) — raw CO2 emissions (log-transformed)**
Raw total CO2 emissions in Gg, log-transformed. We use raw rather than
per-capita to capture total national industrial footprint.
Correlation with log(FCL): r = `r r_cdo_fcl`.

**Development moderator: log(GDP)**
Total GDP log-transformed. Correlation with CDO: r = `r r_cdo_gdp`.
Retained only as additive control or interaction term for EKC testing.

**Industry maturity proxy: HPE**
Human PM2.5 pollution exposure — used as an indicator of how mature and
dense a country's industrial base is. Correlation with log(FCL):
r = `r r_hpe_fcl`.

**Agricultural term: log(SNM) — Sustainable Nitrogen Management Index**
Best agriculture variable by correlation with log(FCL):
r = `r r_snm_fcl`. Relatively independent from CDO (r = `r r_cdo_snm`),
making it a clean addition to test whether agricultural pressure explains
forest loss beyond industrial emissions alone.

---

## Why CDO Alone Represents Industrial Activity

```{r correlation-heatmap, fig.height=5, fig.width=6}
vars <- c("log_CDO", "log_SO2", "log_GDP", "log_POP", "HPE", "SNM", "log_FCL")
cor_matrix <- cor(temp[, vars], use = "complete.obs")
labels <- c("Log CDO", "Log SO2", "Log GDP", "Log POP", "HPE", "SNM", "Log FCL")

rownames(cor_matrix) <- labels
colnames(cor_matrix) <- labels

# Color palette
n <- length(labels)
col_palette <- colorRampPalette(c("steelblue", "white", "coral"))(99)

# Plot heatmap
par(mar = c(5, 8, 4, 2))  # bottom, left, top, right
image(1:n, 1:n, t(cor_matrix[n:1, ]),
      col = col_palette, axes = FALSE,
      xlab = "", ylab = "",
      main = "Correlation Matrix — Selected Variables (2012)")
axis(1, at = 1:n, labels = labels, las = 2)
axis(2, at = 1:n, labels = rev(labels), las = 1)

# Add correlation values
for (i in 1:n) {
  for (j in 1:n) {
    text(j, n - i + 1,
         round(cor_matrix[i, j], 2),
         cex = 0.75, font = 2,
         col = ifelse(abs(cor_matrix[i, j]) > 0.6, "white", "black"))
  }
}
```

---

## Build Analysis Datasets

```{r build-datasets}
library(dplyr)
library(stargazer)

build_year_df <- function(data, year) {
  out <- data.frame(
    country = data$country,
    iso     = data$iso,
    POP     = data[[paste0("POP.raw.", year)]],
    CDO     = data[[paste0("CDO.raw.", year)]],
    SO2     = data[[paste0("SO2.raw.", year)]],
    FCL     = data[[paste0("FCL.raw.", year)]],
    GDP     = data[[paste0("GDP.raw.", year)]],
    GDP_pc  = data[[paste0("GPC.raw.", year)]],
    HPE     = data[[paste0("HPE.raw.", year)]],
    SNM     = data[[paste0("SNM.raw.", year)]]
  )
  # Log transform raw variables
  out$log_CDO <- log(pmax(out$CDO, 1e-10))
  out$log_SO2 <- log(pmax(out$SO2, 1e-10))
  out$log_FCL <- log(pmax(out$FCL, 1e-10))
  out$log_GDP <- log(pmax(out$GDP, 1e-10))
  out$log_POP <- log(pmax(out$POP, 1e-10))
  out$log_SNM <- log(pmax(out$SNM, 1e-10))
  # HPE used as-is (already a rate/index)
  out$year    <- year
  na.omit(out)
}

df_train <- build_year_df(df, 2012)
df_test  <- build_year_df(df, 2021)

cat("Training set (2012):", nrow(df_train), "countries\n")
cat("Test set    (2021):", nrow(df_test),  "countries\n")
```

---

## Exploratory Data Analysis

### Raw vs Log Distributions

```{r eda-dists, fig.height=3.5, fig.width=9}
plot_raw_log_hist <- function(df, raw_col, log_col, label, col) {
  par(mfrow = c(1, 2))
  hist(df[[raw_col]], breaks = 25, col = col, border = NA,
       main = paste0(label, " — Raw"),
       xlab = label)
  abline(v = mean(df[[raw_col]], na.rm = TRUE), col = "red", lwd = 2, lty = 2)
  hist(df[[log_col]], breaks = 25, col = col, border = NA,
       main = paste0("log(", label, ")  |  mean = ",
                     round(mean(df[[log_col]], na.rm = TRUE), 2)),
       xlab = paste0("log(", label, ")"))
  abline(v = mean(df[[log_col]], na.rm = TRUE), col = "red", lwd = 2, lty = 2)
  par(mfrow = c(1, 1))
}

plot_raw_log_hist(df_train, "FCL",  "log_FCL", "Tree Cover Loss (FCL)", "mediumpurple")
plot_raw_log_hist(df_train, "CDO",  "log_CDO", "CO2 Emissions (CDO)",   "steelblue")
plot_raw_log_hist(df_train, "SO2",  "log_SO2", "SO2 Emissions",         "coral")
plot_raw_log_hist(df_train, "GDP",  "log_GDP", "GDP",                   "seagreen")
plot_raw_log_hist(df_train, "POP",  "log_POP", "Population",            "goldenrod")
plot_raw_log_hist(df_train, "HPE", "HPE", "Human PM2.5 Exposure (HPE)", "tomato")
plot_raw_log_hist(df_train, "SNM",  "log_SNM", "Nitrogen Mgmt (SNM)",   "orchid")
```

### Scatterplots: X vs Y

```{r eda-scatter, fig.height=8, fig.width=11}
par(mfrow = c(2, 3))

scatter_fcl <- function(df, xcol, xlabel, col) {
  plot(df[[xcol]], df$log_FCL,
       xlab = xlabel, ylab = "log(Tree Cover Loss)",
       main = paste0(xlabel, " vs FCL  |  r = ",
                     round(cor(df[[xcol]], df$log_FCL, use = "complete.obs"), 3)),
       pch = 19, col = col, cex = 0.8)
  abline(lm(log_FCL ~ df[[xcol]], data = df), col = "red", lwd = 2)
}

scatter_fcl(df_train, "log_CDO", "log(CO2)",       rgb(0.2, 0.4, 0.8, 0.5))
scatter_fcl(df_train, "log_SO2", "log(SO2)",       rgb(0.8, 0.4, 0.2, 0.5))
scatter_fcl(df_train, "log_GDP", "log(GDP)",       rgb(0.2, 0.7, 0.4, 0.5))
scatter_fcl(df_train, "log_POP", "log(Population)",rgb(0.7, 0.6, 0.1, 0.5))
scatter_fcl(df_train, "HPE",     "HPE",            rgb(0.5, 0.2, 0.7, 0.5))
scatter_fcl(df_train, "log_SNM", "log(SNM)",       rgb(0.8, 0.2, 0.5, 0.5))

par(mfrow = c(1, 1))
```

### Correlation Matrix

```{r eda-correlation}
cor_vars <- df_train[, c("log_CDO", "log_SO2", "log_GDP",
                          "log_POP", "HPE", "SNM", "log_FCL")]
round(cor(cor_vars, use = "complete.obs"), 3)
pairs(cor_vars)
```

---

## Models

All models use log(FCL) as the outcome. Raw emissions (CDO) are
log-transformed. Population is included throughout to account for
country size.

### Model 1: log(CDO) + log(POP)

```{r model1}
m1 <- lm(log_FCL ~ log_CDO + log_POP, data = df_train)
summary(m1)
```

### Model 2a: log(CDO) + log(GDP) + log(POP)

```{r model2a}
m2a <- lm(log_FCL ~ log_CDO + log_GDP + log_POP, data = df_train)
summary(m2a)
```

### Model 2b: log(CDO) + log(POP) + HPE

HPE (human PM2.5 pollution exposure) as a proxy for industrial maturity
instead of GDP, which is nearly collinear with CDO.

```{r model2b}
m2b <- lm(log_FCL ~ log_CDO + log_POP + HPE, data = df_train)
summary(m2b)
```

### Model 2c: log(CDO) + log(POP) + HPE + log(SNM)

Adds the best agricultural variable (Sustainable Nitrogen Management
Index) to test whether agricultural pressure explains forest loss beyond
industrial emissions.

```{r model2c}
m2c <- lm(log_FCL ~ log_CDO + log_POP + HPE + SNM, data = df_train)
summary(m2c)
```

### Model 3a: log(CDO) * log(GDP) + log(POP)

Interaction version of Model 2a — tests whether the CDO to FCL
relationship changes with GDP level (EKC hypothesis).

```{r model3a}
m3a <- lm(log_FCL ~ log_CDO * log_GDP + log_POP, data = df_train)
summary(m3a)
```

### Model 3b: log(CDO) * HPE + log(POP)

Interaction version of Model 2b — tests whether the CDO to FCL
relationship changes with industrial maturity level.

```{r model3b}
m3b <- lm(log_FCL ~ log_CDO * HPE + log_POP, data = df_train)
summary(m3b)
```

### Model 3c: log(CDO) * HPE + log(POP) + log(SNM)

Interaction version of Model 2c — adds the agricultural term on top
of the CDO * HPE interaction.

```{r model3c}
m3c <- lm(log_FCL ~ log_CDO * HPE + log_POP + SNM, data = df_train)
summary(m3c)
```

### Model 4: log(CDO) + log(POP) + HPE + SNM + Coastal/Landlocked

Builds on Model 2c by adding a binary geographic indicator for whether
a country is landlocked or coastal. Landlocked countries lack ocean
access and may have different deforestation patterns than coastal nations.

```{r model4}
library(tidyr)

landlocked <- c(
  "Afghanistan", "Armenia", "Azerbaijan", "Bhutan", "Bolivia",
  "Botswana", "Burkina Faso", "Burundi", "Central African Republic",
  "Chad", "Czech Republic", "Ethiopia", "Hungary", "Kazakhstan",
  "Kyrgyzstan", "Laos", "Lesotho", "Luxembourg", "Malawi",
  "Mali", "Moldova", "Mongolia", "Nepal", "Niger",
  "North Macedonia", "Paraguay", "Rwanda", "Serbia",
  "Slovakia", "South Sudan", "Eswatini", "Switzerland",
  "Tajikistan", "Turkmenistan", "Uganda", "Uzbekistan",
  "Zambia", "Zimbabwe", "Austria", "Belarus"
)

df_train$type <- ifelse(df_train$country %in% landlocked, "landlocked", "coastal")
df_test$type  <- ifelse(df_test$country  %in% landlocked, "landlocked", "coastal")

df_train %>% count(type)

vars <- df_train %>%
  select(log_FCL, log_CDO, log_POP, HPE, SNM, type) %>%
  pivot_longer(cols = -type, names_to = "variable", values_to = "value")

ggplot(vars, aes(x = value, fill = type)) +
  geom_histogram(alpha = 0.6, bins = 30, position = "identity") +
  facet_wrap(~variable, scales = "free") +
  theme_minimal() +
  labs(title = "Variable Distributions by Country Type (Coastal vs Landlocked)")

m4 <- lm(log_FCL ~ log_CDO + log_POP + HPE + SNM + type, data = df_train)
summary(m4)
```

### Model 5: log(CDO) + log(POP) + HPE + SNM + Continent

Builds on Model 2c by adding continent as a categorical variable.
Continent captures broad geographic and ecological differences —
tropical continents like Africa and South America have far more
forest cover and deforestation pressure than Europe or Oceania.

```{r model5}
library(countrycode)

df_train$continent <- countrycode(df_train$iso, origin = "iso3c",
                                   destination = "continent")
df_test$continent  <- countrycode(df_test$iso,  origin = "iso3c",
                                   destination = "continent")

m5 <- lm(log_FCL ~ log_CDO + log_POP + HPE + SNM + continent,
         data = df_train)
summary(m5)
```

### Regression Table

```{r regression-table, results='asis'}
stargazer(m1, m2a, m2b, m2c, m3a, m3b, m3c,
          type             = "text",
          title            = "Tree Cover Loss on Industrial Activity (Training Year: 2012)",
          dep.var.labels   = "log(Tree Cover Loss)",
          covariate.labels = c("log(CO2)",
                               "log(GDP)",
                               "log(Population)",
                               "HPE",
                               "log(SNM)",
                               "log(CO2) x log(GDP)",
                               "log(CO2) x HPE"),
          omit.stat        = c("f", "ser"),
          star.cutoffs     = c(0.05, 0.01, 0.001))
```

---

## Model Diagnostics (Model 2c — most complete additive model)

```{r diagnostics, fig.height=7, fig.width=10}
par(mfrow = c(2, 2))
plot(m2c, which = 1, main = "Residuals vs Fitted")
plot(m2c, which = 2, main = "Q-Q Plot")
plot(m2c, which = 3, main = "Scale-Location")
plot(m2c, which = 5, main = "Residuals vs Leverage")
par(mfrow = c(1, 1))
```

```{r assumption-tests}
cat("=== VIF (Model 2c) ===\n")
print(round(vif(m2c), 3))

cat("\n=== Breusch-Pagan Test (Model 2c) ===\n")
print(bptest(m2c))
```

---

## Out-of-Sample Test (2021)

Using Model 2c as the primary evaluation model.

```{r out-of-sample, fig.height=4, fig.width=6}
df_test$predicted <- predict(m2c, newdata = df_test)

rmse_train <- round(sqrt(mean(residuals(m2c)^2)), 4)
rmse_test  <- round(sqrt(mean((df_test$log_FCL - df_test$predicted)^2,
                               na.rm = TRUE)), 4)

ss_res <- sum((df_test$log_FCL - df_test$predicted)^2, na.rm = TRUE)
ss_tot <- sum((df_test$log_FCL - mean(df_test$log_FCL))^2, na.rm = TRUE)
r2_test <- round(1 - ss_res / ss_tot, 4)

cat("RMSE (train, 2012):", rmse_train, "\n")
cat("RMSE (test,  2021):", rmse_test,  "\n")
cat("R2   (train, 2012):", round(summary(m2c)$r.squared, 4), "\n")
cat("R2   (test,  2021):", r2_test, "\n")

plot(df_test$predicted, df_test$log_FCL,
     xlab = "Predicted log(FCL)", ylab = "Actual log(FCL)",
     main = paste0("Out-of-Sample: 2021\n",
                   "RMSE train = ", rmse_train,
                   "  |  RMSE test = ", rmse_test),
     pch = 19, col = rgb(0.2, 0.6, 0.4, 0.6))
abline(0, 1, col = "red", lwd = 2, lty = 2)
```

### Also try to fit the same parameters as model 2c to the test data
```{r model2c_test}
m2c_test <- lm(log_FCL ~ log_CDO + log_POP + HPE + SNM, data = df_test)
summary(m2c_test)
```